module2IVgraphs

### 2023-02-04 combined data set/DVgraphs.Rmd
conducting the Kruskal wallis test on DVs

---
title: "Dependent Variable Graphs"
output:
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
  pdf_document:
    toc: yes
    number_sections: yes
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
---

@@

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(ggbiplot))
suppressPackageStartupMessages(library(psych)) # psychometrics

@@

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2

@@

@@

@@

 center_barplot%>% 
  ggplot(aes(x=technology, y= mean, fill =  (factor(center_barplot$level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
  geom_bar(stat="identity", position=position_dodge())+

@@

>>>>

---
title: "Dependent Variable Graphs"
output:
  pdf_document:
    toc: yes
    number_sections: yes
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(readxl))
suppressPackageStartupMessages(library(hablar))
suppressPackageStartupMessages(library(tsibble))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(DT))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(psych)) # psychometrics

@@

suppressPackageStartupMessages(library(tidyselect))
# combine codedmodule1 and codedmodule2. Therefore these graphs are made on the combined data set from both the surveys.

@@

\newpage

@@

```
\newpage

@@

 center_barplot%>% 
  ggplot(aes(x=technology, y= mean, fill =  (factor(level, levels = c("perceivedrisk.mean", "perceivedbenefit.mean")))))+
  geom_bar(stat="identity", position=position_dodge())+

@@

library(dplyr)
library(tidyr)

perceivedrisk <-joineddf %>% select(starts_with("Risky")) %>%
  gather(key = "technology", value = "perceived_risk") %>% 
  mutate(technology = gsub("Risky_", "", technology)) %>%
  na.omit()

perceivedrisk

```{r}
# checking assumptions for kruskal wallis test

duplicated(joineddf)
sum(duplicated(joineddf))

# there are no duplicate responses in our dataframe :).

ggplot(perceivedrisk, aes(x = perceived_risk, y = technology)) + 
  geom_boxplot()

levels(perceivedrisk$technology)

bartlett.test(perceived_risk ~ technology, data = perceivedrisk)

str(perceivedrisk)

```{r, echo=FALSE}
# create a list of technology levels
tech_levels <- unique(perceivedrisk$technology)

# perform Shapiro test for each technology
shapiro_results <- lapply(tech_levels, function(x) {
  shapiro.test(perceivedrisk$perceived_risk[perceivedrisk$technology == x])
})

#extract the W and p-value from the htest object 
shapiro_results_df <- data.frame(W = sapply(shapiro_results, function(x) x$statistic),
                                  p.value = sapply(shapiro_results, function(x) x$p.value), 
                                  technology = tech_levels)

```{r}
# load the stats package
library(stats)

perceivedrisk$technology <- factor(perceivedrisk$technology)

# perform the Kruskal-Wallis H-test, the technologies are treated as independent groups and the mean of perceived risk is of interest. 
kruskal_result <- kruskal.test(perceived_risk ~ technology, data = perceivedrisk)

# print the test statistic and p-value
print(kruskal_result)

library(emmeans)
emm_results <- emmeans(kruskal_results, ~ technology)
summary(emm_results, infer = c(T, T))

```{r}

library(dplyr)
ggplot(perceivedrisk %>%
  mutate(technology = reorder(technology, perceived_risk, FUN = median)), 
         aes(x = technology, y = perceived_risk)) +
  geom_boxplot(width = 0.5) +
  geom_hline(aes(yintercept = median(perceived_risk)), linetype = "dashed", color = "red") +
  coord_flip()

```{r}
library(dplyr)
perceivedrisk %>%
  group_by(technology) %>%
  summarise(
    count = n(),
    mean = mean(perceived_risk, na.rm = TRUE),
    sd = sd(perceived_risk, na.rm = TRUE),
    median = median(perceived_risk, na.rm = TRUE),
    IQR = IQR(perceived_risk, na.rm = TRUE)
  )

```
```{r}

pairwise.wilcox.test(perceivedrisk$perceived_risk, perceivedrisk$technology, p.adjust.method = "BH")

```{r}

# visualising the pairwaise wilcox test results. the non significant pairs are grey

library(broom)
result <- pairwise.wilcox.test(perceivedrisk$perceived_risk, perceivedrisk$technology, p.adjust.method = "BH")
tidy_result <- tidy(result)

library(ggplot2)
ggplot(tidy_result, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "red", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "Technology 1", y = "Technology 2") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```{r}
#now do the same for perceived benefit
#null hypothesis - no sognificant difference between perceived benefit from technologies. 
#push to github - figure out what happened! why not pushing anymore yaar 
#

```{r, echo=FALSE}
library(dplyr)
library(tidyr)

perceivedbenefit <-joineddf %>% select(starts_with("Ben")) %>%
  gather(key = "technology", value = "perceived_benefit") %>% 
  mutate(technology = gsub("Ben_", "", technology)) %>%
  na.omit()

perceivedbenefit

```{r}
# checking assumptions for kruskal wallis test

duplicated(joineddf)
sum(duplicated(joineddf))

# there are no duplicate responses in our dataframe :).

#what was I doing here - check again ? assumptions for running it on perceived benefit

ggplot(perceivedbenefit, aes(x = perceived_benefit, y = technology)) + 
  geom_boxplot()

levels(perceivedbenefit$technology)

bartlett.test(perceived_benefit ~ technology, data = perceivedbenefit)

str(perceivedbenefit)

```{r}
# load the stats package
library(stats)

perceivedbenefit$technology <- factor(perceivedbenefit$technology)

# perform the Kruskal-Wallis H-test, the technologies are treated as independent groups and the mean of perceived risk is of interest. 
kruskal_resultben <- kruskal.test(perceived_benefit ~ technology, data = perceivedbenefit)

# print the test statistic and p-value
print(kruskal_resultben)

```{r}

library(dplyr)
ggplot(perceivedbenefit %>%
  mutate(technology = reorder(technology, perceived_benefit, FUN = median)), 
         aes(x = technology, y = perceived_benefit)) +
  geom_boxplot(width = 0.5) +
  geom_hline(aes(yintercept = median(perceived_benefit)), linetype = "dashed", color = "red") +
  coord_flip()

```
```{r}
library(dplyr)
perceivedbenefit %>%
  group_by(technology) %>%
  summarise(
    count = n(),
    mean = mean(perceived_benefit, na.rm = TRUE),
    sd = sd(perceived_benefit, na.rm = TRUE),
    median = median(perceived_benefit, na.rm = TRUE),
    IQR = IQR(perceived_benefit, na.rm = TRUE)
  )

```{r}

pairwise.wilcox.test(perceivedbenefit$perceived_benefit, perceivedbenefit$technology, p.adjust.method = "BH")

```{r}

# visualising the pairwaise wilcox test results. the non significant pairs are grey

library(broom)
result <- pairwise.wilcox.test(perceivedbenefit$perceived_benefit, perceivedbenefit$technology, p.adjust.method = "BH")
tidy_result <- tidy(result)

library(ggplot2)
ggplot(tidy_result, aes(x = group1, y = group2, fill = p.value)) + 
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "green", high = "white", midpoint = 0.025, 
                       limits = c(0, 0.05), space = "Lab", 
                       name = "P-value") + 
  theme_classic() + 
  labs(x = "Technology 1", y = "Technology 2") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

### 2023-02-04 combined data set/demographicvariables.Rmd
conducting the Kruskal wallis test on DVs

## Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups

@@

caste_genderh%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")
```
## Perceived Benefit Scores for centrally managed hydroelectric dams by gender and caste groups

@@

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

@@

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

@@

@@

## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.

@@

@@

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

>>>>

\newpage
## Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups

@@

caste_genderh%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")
```

\newpage

## Perceived Benefit Scores for centrally managed hydroelectric dams by gender and caste groups

@@

\newpage
## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

@@

\newpage
## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

@@

\newpage

## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.

@@

\newpage
## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.

@@

\newpage

## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.

@@

\newpage
## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

### 2023-02-04 module2/module2IVgraphs.Rmd
conducting the Kruskal wallis test on DVs

---
title: "module2IVgraphs"
output: 
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged

@@

    toc: true
    number_sections: true
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
---

@@

# **Coded Dataset for survey module 2**
```{r, echo = FALSE}

@@

data.frame(codedmodule2)

@@

# **Perceived risk by Support for decentralised governance**

>>>>

---
title: "module2IVgraphs"
output:

@@

    toc: true
    number_sections: true
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

```{r, echo = FALSE}

@@

@@

\newpage
# **Perceived risk by Support for decentralised governance**
